%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Jacob Stinnett}} &   \href{mailto:stinnettjacob@gmail.com}{stinnettjacob@gmail.com}\\
 {PhD Candidate, NRC Research Fellow} &  405.509.4584 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Urbana, IL}
      {PhD in Nuclear, Plasma, and Radiological Engineering}{Fall 2016}
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Urbana, IL}
      {MS in Nuclear, Plasma, and Radiological Engineering}{May 2014}
    \resumeSubheading
      {University of Oklahoma}{Norman, OK}
      {BS in  Physics and BA in Mathematics}{May 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Urbana, IL}
      {NRC Research Fellow}{May 2013- Present}
      \resumeItemListStart
        \resumeItem{Isotope Identification}
          {Developed various Bayesian classifiers for automated isotope identification on low-resolution gamma-ray detectors.}
        \resumeItem{Library Generation}
          {Created method to generate tailored isotope libraries for different detectors that is coupled to the feature extraction method. }
        \resumeItem{Spectra Simulations}
          {Simulated detector response functions for arbitrary radiation energy.  Built Python code to generate pseudospectra for arbitrary gamma-ray sources.}
        \resumeItem{Feature Extraction}
          {Various contributions to a wavelet/NNLS feature extraction code, including line-detection routines and porting the code to Python.}
        \resumeItem{Neural Networks}
          {Wrote a simulated annealing training method in MATLAB and showed proof of concept for using NNs for spectra classification.}
      \resumeItemListEnd

    \resumeSubheading
      {Los Alamos National Laboratory}{Los Alamos, NM}
      {Guest Scientist}{Summer 2015}
      \resumeItemListStart
        \resumeItem{Neutron simulations}
          {Built simulations in MCNP for neutron flux calculations for nuclear threat detection scenarios.}
        \resumeItem{Gamma spectroscopy}
          {Measured spectra of Category I quantities of special nuclear materials at the Nevada National Security Site.}
      \resumeItemListEnd
      
 \resumeSubheading
      {University of Illinois at Urbana-Champaign}{Urbana, IL}
      {Teaching Assistant}{August 2012- May 2013}
      \resumeItemListStart
        \resumeItem{NPRE451 Nuclear Radiations Lab}
          {Led a lab section covering nuclear instrumentation, radiation data analysis, and nuclear safety.    }
        \resumeItem{NPRE446 Interactions of Radiation with Matter}
          {Head TA for course on classical and quantum mechanics for engineers, with emphasis on neutron and electron interactions.}
      \resumeItemListEnd



    \resumeSubheading
      {University of Oklahoma}{Norman, OK}
      {Undegraduate Research Assistant}{Jan 2009 - May 2012}
      \resumeItemListStart
        \resumeItem{Diatomic Spectroscopy}
          {Performed calculations and simulations of a NO-He van der Waals complex to explain experimental observation of a linear Stark effect in NO. Built laboratory hardware and operated laser optics.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

% Publications
\section{Selected Papers and Presentations}

  \resumeSubHeadingListStart
    \resumeSubItem{Performance of an Automated Isotope Identification Algorithm for Handheld NaI Detectors}
      {J. Stinnett and C.J. Sullivan.  \textit{IEEE Nuclear Science Symposium Conference Record.} \hfill 2015}
    \resumeSubItem{Validation of a Bayesian-Based Isotope Identification Algorithm}
      {C.J. Sullivan and J. Stinnett.  \textit{Nuclear Instruments and Methods in Physics Research A.} \hfill 2014}
    \resumeSubItem{Investigation of the Use of He-Diatomic Van Der Waals Complexes as a Probe of Time-Reversal Violation}
      {J. Stinnett, E. Abraham, N. Shafer-Ray. \textit{66th Symposium on Molecular Spectroscopy.} \hfill 2011}
  \resumeSubHeadingListEnd




%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
%\textbf{Python, MATLAB, Wolfram Language, MCNP}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, MATLAB, Wolfram Language}
      \hfill
      \textbf{Technologies}{: MCNP}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}