% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.34in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\addtolength{\topmargin}{-.26in}
\addtolength{\oddsidemargin}{-.15in}
\addtolength{\evensidemargin}{-.15in}
\addtolength{\textheight}{3cm}


%\addtolength{\topmargin}{-.56in}
%\addtolength{\oddsidemargin}{-.35in}
%\addtolength{\evensidemargin}{-.5in}
%\addtolength{\voffset}{0cm}
%\addtolength{\textheight}{5cm}

%\addtolength{\bottom}{-.25in}

\begin{document} 
 \name{Jacob Stinnett\\[12pt]} % the \\[12pt] adds a blank line after name

% \address{{\bf Office Address} \\ 104 S. Wright St, Room 119 \\ Urbana, IL 61820\\ (405)509.4584 \\ stinntt2@illinois.edu }
 
\address{{\bf Home Address} \\ 2403 W. Springfield Ave, Apt Y6  \\ Champaign, IL \\ 61821 }
\address{{\bf Contact} \\ e-mail: stinnettjacob@gmail.com  \\ website: stinnett.github.io  \\ (405)509.4584 }


 
\begin{resume} 
 
%\section{Objective} 
%Auditing/Analysis of Operations 

\section{Education} 
Ph.D. in Nuclear, Plasma, and Radiological Engineering, University of\ Illinois at Urbana-Champaign.   \hspace{3.9in} \textbf{Oct 2016}

\begin{itemize}
\item ``Automated Isotope Identification Algorithms for Low-Resolution Gamma Spectrometers.''
\item Advisor: Professor Clair J. Sullivan
\end{itemize}

\vspace{-.05in}

M.S. in Nuclear, Plasma, and Radiological Engineering, University of\ Illinois at Urbana-Champaign  \hfill \textbf{2014}

\vspace{-.05in}

B.S. in Physics and B.A. in Mathematics, University of Oklahoma \hfill  \textbf{2012}
 

\section{Experience}

 {\bf Research Fellow,} UIUC, Urbana, IL \hfill \textbf{May 2013-Present}
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item Developed Bayesian classifier algorithms for automated isotope identification
\item Developed algorithm to create isotope libraries for low-resolution detectors that are customized for arbitrary feature extraction methods
 \item Built gamma spectra simulation software in Python using MCNP-generated detector response functions
 \item Wrote neural network training algorithm and performed proof of concept of using neural networks for low-resolution spectra classification
 \end{itemize} 
 
 
 {\bf Guest Scientist,} Los Alamos National Labratory, Los Alamos, NM \hfill \textbf{Summer 2015}
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item MCNP6 neutron simulations in A-2 division
 \item Gamma spectroscopy measurements at Nevada National Security Site
 \end{itemize} 
 
\vspace{-.05in}
 
   {\bf Teaching Assistant,} UIUC, Urbana, IL \hfill \textbf{Aug 2012- May 2013}
 \begin{itemize} \itemsep -3pt  % reduce space between items
 \item Nuclear Radiations Laboratory (NPRE 451)
 \item Interaction of Radiation with Matter (NPRE 446)
 \end{itemize}

\vspace{-.05in}
 
 {\bf Various Research Experiences,} University of Oklahoma, Norman, OK \hfill  \textbf{2009-2012}
\begin{itemize} \itemsep -3pt %reduce space between items
\item Undergraduate Research Assistant to Dr. Shafer-Ray: performed calculations and simulations of an NO-He van der Waals complex to explain experimental observation of a linear Stark effect
\item NSF Research Experience for Undergraduates: assisted in diatomic molecular spectroscopy experiments, built electronics, and set up laser systems
\item Undergraduate research: nonlinear dynamics theory and simulations
\end{itemize}

\vspace{-.05in}


%\section{Skills}

\section{Publications}
%J. Stinnett and C.J. Sullivan.  ``An Automated Isotope Identification Algorithm using Bayesian Statistics.''  \textit{IEEE Transactions on Nuclear Science}, In Publication. \hfill 2014
%

J. Stinnett , M.M. Watson, C.J. Sullivan, and H. Xiong. `'Feature Extraction and Isotope Identification on NaI Gamma-Ray Spectra.'' \textit{IEEE Transactions on Nuclear Science}. In review. \hfill \textbf{2016}

M. Kamuda, J. Stinnett, and C.J. Sullivan . Automated Isotope Identification Algorithm Using Artificial Neural Networks. \textit{IEEE Transactions on Nuclear Science}. In review. \hfill \textbf{2016}

J. Mattingly, J. Hutchinson, C. Sullivan, J. Stinnett , M. Kamuda, M. Alamaniotis, B. Simms, J. Mueller, J. Newby, J. Linkous, S. Pozzi, K. Polack, M. Hamel, Z. He, D. Goodman, and M. Streicher.  "CNEC and CVT Subcritical Experiments with Category I Special Nuclear Material at the Nevada National Security Site Device Assembly Facility." \textit{Institute of Nuclear Materials Management Conference Record}. In review. \hfill \textbf{2016}

J. Stinnett and C.J. Sullivan.  ``Performance of an Automated Isotope Identification Algorithm for Handheld NaI Detectors.''  \textit{IEEE Nuclear Science Symposium Conference Record}   \hfill \textbf{2015}

C.J. Sullivan and J. Stinnett.  ``Validation of a Bayesian-Based Isotope Identification Algorithm.''  \textit{Nuclear Instruments and Methods in Physics Research A.}   \hfill \textbf{2014}

\vspace{-.05in}

J. Stinnett.  ``Bayesian Algorithms for Automated Isotope Identification''.  \textit{MS Thesis}.  University of Illinois at Urbana-Champaign. \hfill \textbf{2014}

\vspace{-.05in}

J. Stinnett, C.J. Sullivan, "An Automated Isotope Identification Algorithm Using Bayesian Statistics," IEEE Nuclear Science Symposium Conference Record. \hfill \textbf{2013}

\section{Conference Presentations}
J. Stinnett , M.M. Watson, C.J. Sullivan, and H. Xiong. `'Feature Extraction and Isotope Identification on NaI Gamma-Ray Spectra.'' \textit{IEEE Nuclear NSS/MIC}. San Diego, CA.  \hfill \textbf{2015}

J. Stinnett and C.J. Sullivan.  ``Automated Isotope Identification of Single-Source and Mixed-Sources.''  \textit{IEEE Nuclear NSS/MIC}. San Diego, CA.  \hfill \textbf{2015}

J. Stinnett and C.J. Sullivan.  ``Automated Isotope Identification of Single-Source and Mixed-Sources.''  \textit{IEEE Nuclear NSS/MIC}. Seattle, WA.  \hfill \textbf{2014}

J. Stinnett and C.J. Sullivan.  ``Validation of a Bayesian-Based Isotope Identification Algorithm.'' \textit{SORMA.}  Ann Arbor, MI. \hfill \textbf{2014}

\vspace{-.05in}

J. Stinnett and C.J. Sullivan.  ``An Automated Isotope Identification Algorithm using Bayesian Statistics.''  \textit{IEEE Nuclear NSS/MIC}. Seoul, South Korea.  \hfill \textbf{2013}

\vspace{-.05in}

J. Stinnett, E. Abraham, N. Shafer-Ray.  "Investigation of the Use of NO-He Diatomic Van der Waals Complexes as a Probe of Time-Reversal Violation". \textit{ 66$^{th}$ Ohio State University International Symposium on Molecular Spectroscopy}, Columbus, OH. \hfill \textbf{2011}

\section{Academic \\ Honors} 
NRC/UIUC Nuclear Engineering Fellow \hfill \textbf{2014} \\
National Merit Scholar \hfill \textbf{2008-2012} \\
Duane E. Roller Award for Outstanding Scholarship in Physics and Astronomy \hfill \textbf{2011}

\section{Programming}
Python, MATLAB, Mathematica, MCNP, LaTeX
 
\end{resume} 
\end{document} 



